An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-11 EconGrowth.Rnw
Added code to calculate AIC values for the CES production function. However, it doesn't work at the present time, so it is commented out.
Added a comment on the status of the AIC code for CES in the to-do list of the paper.
Rearranged authors and acknowledgements.

\author[Calvin]{Caleb Reese}
\author[Calvin]{Lucas Timmer}
\author[Stellenbosch]{Martin de Wit}
\author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}

\cortext[cor1]{Corresponding author}
\address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
\address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}

@@

\section*{To-do List}
\begin{itemize}
\item Reese: Add text from Word verson of paper to the LaTeX version.
\item Heun: Add CES production function fits
      \begin{itemize}
      \item \st{GDP comparison graph}
      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
      \item Write up the decisions about parameter estimation for the CES production function fits
      \item \st{Create parameter graphs for each country}
      \item \st{Parameter tables for each energy type in the appendix}
      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
      \item AIC rows in the AIC table
      \item \st{Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
      \end{itemize}
\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
      \begin{itemize}
      \item Zambia, upper bound on $c_t$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
\item de Wit: provide funding acknowledgement, if necessary.
\item de Wit: review, critique, and contextualize.
\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: Move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\item \st{Heun: Add single factor fits}
      \begin{itemize}
      \item \st{Correct sizes for parameter graphs for each country}
      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{GDP comparison graph}
      \item \st{AIC rows in the AIC table}
      \end{itemize}
\item \st{Heun: Add setup variables for figure height and width where not already included.}
\item \st{Heun: Add LINEX production function fits}
      \begin{itemize}
      \item \st{Parameter graphs for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{AIC rows in the AIC table}
      \item \st{GDP comparison graph}
      \end{itemize}
\end{itemize}

@@

Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association. Funding for Martin de Wit was provided by *******. The authors thank Randall Pruim (Calvin College) and Loren L. Heun (Western Michigan University) for their insightful comments on and invaluable assistance with the statistical analyses presented herein.
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
%% \section{}
%% \label{}

>>>>

\author[CalvinEngr]{Caleb Reese}
\author[CalvinEngr]{Lucas Timmer}
\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
\author[Stellenbosch]{Martin de Wit}
\author[CalvinMath]{Randall J. Pruim}
\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}

\cortext[cor1]{Corresponding author}
\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
\address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}

@@

\section*{To-do List}
\begin{itemize}
\item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.
\item Heun: Add CI vs. params plots for all model types. Maybe as a lattice graph where each model type is a panel.
\item Heun: Add CES production function fits
      \begin{itemize}
      \item \st{GDP comparison graph}
      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
      \item Write up the decisions about parameter estimation for the CES production function fits
      \item \st{Create parameter graphs for each country}
      \item \st{Parameter tables for each energy type in the appendix}
      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
      \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)
      \item \st{Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
      \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
      \end{itemize}
\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
      \begin{itemize}
      \item Zambia, upper bound on $c_t$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
\item de Wit: provide funding acknowledgement, if necessary.
\item de Wit: review, critique, and contextualize.
\item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: Move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\item \st{Heun: Add single factor fits}
      \begin{itemize}
      \item \st{Correct sizes for parameter graphs for each country}
      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{GDP comparison graph}
      \item \st{AIC rows in the AIC table}
      \end{itemize}
\item \st{Heun: Add setup variables for figure height and width where not already included.}
\item \st{Heun: Add LINEX production function fits}
      \begin{itemize}
      \item \st{Parameter graphs for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{AIC rows in the AIC table}
      \item \st{GDP comparison graph}
      \end{itemize}
\end{itemize}

@@

Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association. A Calvin Research Fellowship provided funding for Matthew Kuperus Heun. Funding for Martin de Wit was provided by *******. The authors thank Loren L. Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
%% \section{}
%% \label{}
